# Regression Models Course Project

##Summary<br>
**In this analysis we wish to study the effect of transmission on miles per gallon.We conducted t test which alludes that there is significant difference in mpg for  automatic and manual tranmission.**  

**The fitted model suggest that estimated mpg for manual transmission is 2.9358  more than  the estimated mpg for automatic transmission,provided the other variables are kept constant.**
<br>

### Data processing<br>
```{r}
library(dplyr)
library(ggplot2)
data(mtcars)
mtcars$am<-as.factor(mtcars$am)
levels(mtcars$am)=c("at","mt")

```
The mtcars dataset has been loaded to be analysed.The column am(transmission) has been tranformed into factor with levels at(automatic) and mt(manual).<br>

### Exploratory Data Analysis.<br>
In this analysis we specifically wish to answer the question-Is an automatic or manual transmission better for MPG?.Hence our exploratory analysis will revolve aroung mpg and am(transmission).<br>
```{r}
pairs(mtcars,col="blue")

```

The above pair plot shows potential relationships between different variables of the mtcars dataset.

```{r}
str(mtcars)
ggplot(mtcars,aes(am,mpg,fill=am))+geom_boxplot()+labs(x="Transmission")+labs(y="miles per gallon")+labs(title="Camparison of miles per gallon for different transmissions.")
```

*Miles per gallon seems to differ according to transmission.Hence formal inference should be conducted over this idea.*<br>

### Formal Hypothesis testing<br>
```{r}
mpg_at<-select(filter(mtcars,am=="at"),mpg)
mpg_mt<-select(filter(mtcars,am=="mt"),mpg)
t.test(mpg_at,mpg_mt)
```

The p value is less than 0.05 and hence we fail to accept the null hypothesis.The T test alludes to statistically significant difference between mpg of automatic and manual transmission.<br>

### Linear Models<br>
**Model 1**

```{r}
fit1<-lm(mpg~am,data=mtcars)
summary(fit1)
```

In this models both the intercept and coefficient are statistically significant.Acoording to the model the estimated mpg for manual transmission is 7.245 more than the automatic transmission.The R^2 of the model is 0.3598,which alludes that this model only explains 35.98% of the relationship.<br>

**Model 2**

```{r}
fit2<-step(lm(mpg~.,data=mtcars),trace=0)
summary(fit2)
```

The step algorithm picks the variables which have highest effect on the mpg for the model.Acoording to this model transmission,weight and qsec(1/4 mile time) seems to have highest effect on mpg.<br>
*This model suggests that mpg for manual transmission is 2.9358 more than mpg of automatic transmission,provided the other variables are kept constant.*<br>
The adjusted R^2 suggests that around 83.36% of the relationship is explained by the model.<br>

### Anova testing<br>

```{r}
anova(fit1,fit2)
```

According to the anova testing,fit2 is signifiantly better model tha fit1.It explains around 83.36% of the  relationship.<br>

### Residual testing for the chosen model.

residual plots<br>
```{r}
par(mfrow=c(2,2))
plot(fit2)
```

There does not seem to be any pattern between residuals and the fitted value and residuals seems to follow normal distribution.<br>

**Shapiro wilk test**<br>
```{r}
shapiro.test(fit2$residuals)
```

The p value is 0.08043 and hence we fail to reject the null hypothesis.The null hypothesis suggest the normality of the residuals.<br>

## Conclusion<br>
**The fitted model suggest that estimated mpg for manual transmission is 2.9358 more than the estimated mpg for automatic transmission,when other variables are kept constant.**





